List of Items

### 2020-04-23 items.Rmd
created new file "analyses additional"

---
title: "A Longitudinal Analysis of the Privacy Paradox"
author: "Tobias Dienlin, Philipp K. Masur, Sabine Trepte"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 5
    df_print: paged
editor_options: 
  chunk_output_type: inline
---

```{r, echo=F, include=F}
# defaults
set.seed(170819)
options(digits=3, width=120, max.print=100000)
knitr::opts_chunk$set(echo=T, error=F, message=F, tidy=T, warning=F, cache=F)
```

```{r Packages, include=F, cache=F}
# relevant packages
devtools::install_github("tdienlin/td@v.0.0.2.5")
required <- c("GGally", "ggplot2", "lavaan", "lme4", "magrittr", 
              "MissMech", "papaja", "psych", "pwr", "MVN", "semTools", 
              "sjstats", "tidyverse", "td")

# load required libraries
lapply(required, function(x) library(x, character.only = T))

# export bib library
r_refs("../bibliography/r-references.bib")
```

```{r datawrangling, include=F}
# first run "data_wranling.R", in order to create these objects
d_wide <- read_csv("../data/data_wide.csv")
d_wide_all <- read_csv("../data/data_wide_all.csv")
d_long <- read_csv("../data/data_long.csv")
```

```{r include=F}
# Extract descriptives to report in paper
desc <- d_wide %>% 
  summarize_at(vars(ends_with("_m")), funs(mean(., na.rm = TRUE), sd(., na.rm = TRUE)))
```

@@

# Power Analyses

```{r power}
n_complete <- nrow(d_wide)
alpha <- .05
power <- .95
sesoi <- .1
n <- n_complete
n_apriori <- pwr.r.test(r = sesoi, sig.level = alpha, power = power)$n
power_achieved_h <- pwr.r.test(r = sesoi, sig.level = alpha, n = n, alternative = "greater")$power
alpha_balanced_h <- balance_errors(sesoi, n, one_tailed = TRUE)
power_balanced_h <- 1 - alpha_balanced_h
power_achieved_rq <- pwr.r.test(r = sesoi, sig.level = alpha, n = n)$power
alpha_balanced_rq <- balance_errors(sesoi, n, one_tailed = FALSE)
power_balanced_rq <- 1 - alpha_balanced_rq
```

A-priori power analyses revealed that N = `r n_apriori` people would be needed to find effects with a size of _r_ = `r sesoi` with a power of `r power`.

Overall, the data of `r n` respondents could be used for our analyses. As a result, alpha and beta errors were balanced when using an alpha of `r alpha_balanced_h %>% round(3)`, resulting in an achieved power of `r power_balanced_h %>% round(3)`.

# Sociodemographics

```{r}
age_m <- mean(d_wide$age)
age_sd <- sd(d_wide$age)
male_per <- mean(d_wide$male)
edu_col_per <- nrow(d_wide[d_wide$edu_num > 5, ]) / n_complete * 100
```

# Analysis of Missing Values

```{r cache=F}
d_tmp <- select(d_wide, -contains("_m"), -contains("tim"), -contains("T4"), -contains("T5"), -contains("per"), -contains("use"), -c(id, age, edu, edu_num, male))
test_mar <- TestMCARNormality(d_tmp)

# print patterns
as.data.frame(test_mar$patused)

# non-parametric test
(test_mar_p <- test_mar$pnormality)

# calculate percentage of missing data
na_per <- mean(c(d_wide$t1_na_per, d_wide$t2_na_per, d_wide$t3_na_per)) * 100
```

Visual inspection of the missing value patterns as well as the non-parametric test suggested that all missing values could be considered to be missing at random (_p_ `r test_mar$pnormality %>% td::my_round("p_txt")`).

# Factor Analyses
## Concerns about online privacy
### EFA

```{r}
# set-up
no <- 0
name <- "pri_con"
d_tmp <- select(d_wide, contains(paste0("t1_", name)), -contains("_m"))
model <- fa.parallel(d_tmp, fa = "fa", fm = "ml")
factan <- fa(d_tmp, fm = "ml", nfactors = model$nfact, rotate = "promax")
print(factan, sort = TRUE, cut = .3)
```

### CFA
#### First-Order Model Unconstrained

```{r}
model <- '
# create factors
t1_pri_con_f =~ 1*t1_pri_con_01 + t1_pri_con_02 + t1_pri_con_03 + t1_pri_con_04 + t1_pri_con_05 + t1_pri_con_06 + t1_pri_con_07 + t1_pri_con_08 + t1_pri_con_09
t2_pri_con_f =~ 1*t2_pri_con_01 + t2_pri_con_02 + t2_pri_con_03 + t2_pri_con_04 + t2_pri_con_05 + t2_pri_con_06 + t2_pri_con_07 + t2_pri_con_08 + t2_pri_con_09
t3_pri_con_f =~ 1*t3_pri_con_01 + t3_pri_con_02 + t3_pri_con_03 + t3_pri_con_04 + t3_pri_con_05 + t3_pri_con_06 + t3_pri_con_07 + t3_pri_con_08 + t3_pri_con_09

# error covariances
t3_pri_con_01 ~~ t2_pri_con_01 + t1_pri_con_01
t3_pri_con_02 ~~ t2_pri_con_02 + t1_pri_con_02
t3_pri_con_03 ~~ t2_pri_con_03 + t1_pri_con_03
t3_pri_con_04 ~~ t2_pri_con_04 + t1_pri_con_04
t3_pri_con_05 ~~ t2_pri_con_05 + t1_pri_con_05
t3_pri_con_06 ~~ t2_pri_con_06 + t1_pri_con_06
t3_pri_con_07 ~~ t2_pri_con_07 + t1_pri_con_07
t3_pri_con_08 ~~ t2_pri_con_08 + t1_pri_con_08
t3_pri_con_09 ~~ t2_pri_con_09 + t1_pri_con_09
t2_pri_con_01 ~~ t1_pri_con_01
t2_pri_con_02 ~~ t1_pri_con_02 
t2_pri_con_03 ~~ t1_pri_con_03
t2_pri_con_04 ~~ t1_pri_con_04
t2_pri_con_05 ~~ t1_pri_con_05 
t2_pri_con_06 ~~ t1_pri_con_06
t2_pri_con_07 ~~ t1_pri_con_07
t2_pri_con_08 ~~ t1_pri_con_08
t2_pri_con_09 ~~ t1_pri_con_09

# factor covariances
t1_pri_con_f ~~ t2_pri_con_f + t3_pri_con_f
t2_pri_con_f ~~ t3_pri_con_f
'
no <- no + 1
assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
reliability(get(paste("fit", name, no, sep = "_")))
```

#### First-Order Model Constrained

```{r}
model <- '
# create factors
t1_pri_con_f =~ 1*t1_pri_con_01 + b2*t1_pri_con_02 + b3*t1_pri_con_03 + b4*t1_pri_con_04 + b5*t1_pri_con_05 + b6*t1_pri_con_06 + b7*t1_pri_con_07 + b8*t1_pri_con_08 + b9*t1_pri_con_09
t2_pri_con_f =~ 1*t2_pri_con_01 + b2*t2_pri_con_02 + b3*t2_pri_con_03 + b4*t2_pri_con_04 + b5*t2_pri_con_05 + b6*t2_pri_con_06 + b7*t2_pri_con_07 + b8*t2_pri_con_08 + b9*t2_pri_con_09
t3_pri_con_f =~ 1*t3_pri_con_01 + b2*t3_pri_con_02 + b3*t3_pri_con_03 + b4*t3_pri_con_04 + b5*t3_pri_con_05 + b6*t3_pri_con_06 + b7*t3_pri_con_07 + b8*t3_pri_con_08 + b9*t3_pri_con_09

# error covariances
t3_pri_con_01 ~~ t2_pri_con_01 + t1_pri_con_01
t3_pri_con_02 ~~ t2_pri_con_02 + t1_pri_con_02
t3_pri_con_03 ~~ t2_pri_con_03 + t1_pri_con_03
t3_pri_con_04 ~~ t2_pri_con_04 + t1_pri_con_04
t3_pri_con_05 ~~ t2_pri_con_05 + t1_pri_con_05
t3_pri_con_06 ~~ t2_pri_con_06 + t1_pri_con_06
t3_pri_con_07 ~~ t2_pri_con_07 + t1_pri_con_07
t3_pri_con_08 ~~ t2_pri_con_08 + t1_pri_con_08
t3_pri_con_09 ~~ t2_pri_con_09 + t1_pri_con_09
t2_pri_con_01 ~~ t1_pri_con_01
t2_pri_con_02 ~~ t1_pri_con_02 
t2_pri_con_03 ~~ t1_pri_con_03
t2_pri_con_04 ~~ t1_pri_con_04
t2_pri_con_05 ~~ t1_pri_con_05 
t2_pri_con_06 ~~ t1_pri_con_06
t2_pri_con_07 ~~ t1_pri_con_07
t2_pri_con_08 ~~ t1_pri_con_08
t2_pri_con_09 ~~ t1_pri_con_09

# factor covariances
t1_pri_con_f ~~ t2_pri_con_f + t3_pri_con_f
t2_pri_con_f ~~ t3_pri_con_f
'
no <- no + 1
assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
```

#### Second-Order Model Unconstrained

In what follows, we analyze a second-order solution of privacy concerns. Here, we distinguish between horizontal privacy concerns (items 4, 5, 6) and vertical privacy concerns (items 7, 8, 9). The resulting model fits the data better than the unidimensional one.

```{r}
model <- '
# create factors
t1_pri_con_f =~ 1*t1_pri_con_f1 + t1_pri_con_f2
t2_pri_con_f =~ 1*t2_pri_con_f1 + t2_pri_con_f2
t3_pri_con_f =~ 1*t3_pri_con_f1 + t3_pri_con_f2
t1_pri_con_f1 =~ 1*t1_pri_con_04 + t1_pri_con_05 + t1_pri_con_06
t1_pri_con_f2 =~ 1*t1_pri_con_07 + t1_pri_con_08 + t1_pri_con_09
t2_pri_con_f1 =~ 1*t2_pri_con_04 + t2_pri_con_05 + t2_pri_con_06
t2_pri_con_f2 =~ 1*t2_pri_con_07 + t2_pri_con_08 + t2_pri_con_09
t3_pri_con_f1 =~ 1*t3_pri_con_04 + t3_pri_con_05 + t3_pri_con_06
t3_pri_con_f2 =~ 1*t3_pri_con_07 + t3_pri_con_08 + t3_pri_con_09

# error covariances
t3_pri_con_04 ~~ t2_pri_con_04 + t1_pri_con_04
t3_pri_con_05 ~~ t2_pri_con_05 + t1_pri_con_05
t3_pri_con_06 ~~ t2_pri_con_06 + t1_pri_con_06
t3_pri_con_07 ~~ t2_pri_con_07 + t1_pri_con_07
t3_pri_con_08 ~~ t2_pri_con_08 + t1_pri_con_08
t3_pri_con_09 ~~ t2_pri_con_09 + t1_pri_con_09
t2_pri_con_04 ~~ t1_pri_con_04
t2_pri_con_05 ~~ t1_pri_con_05 
t2_pri_con_06 ~~ t1_pri_con_06
t2_pri_con_07 ~~ t1_pri_con_07
t2_pri_con_08 ~~ t1_pri_con_08
t2_pri_con_09 ~~ t1_pri_con_09

# factor covariances
t1_pri_con_f ~~ t2_pri_con_f + t3_pri_con_f
t2_pri_con_f ~~ t3_pri_con_f
'
no <- no + 1
assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
```

#### Second-Order Model Constrained

```{r}
model <- '
# create factors
t1_pri_con_f =~ 1*t1_pri_con_f1 + a2*t1_pri_con_f2
t2_pri_con_f =~ 1*t2_pri_con_f1 + a2*t2_pri_con_f2
t3_pri_con_f =~ 1*t3_pri_con_f1 + a2*t3_pri_con_f2
t1_pri_con_f1 =~ 1*t1_pri_con_04 + b2*t1_pri_con_05 + b3*t1_pri_con_06
t1_pri_con_f2 =~ 1*t1_pri_con_07 + c2*t1_pri_con_08 + c3*t1_pri_con_09
t2_pri_con_f1 =~ 1*t2_pri_con_04 + b2*t2_pri_con_05 + b3*t2_pri_con_06
t2_pri_con_f2 =~ 1*t2_pri_con_07 + c2*t2_pri_con_08 + c3*t2_pri_con_09
t3_pri_con_f1 =~ 1*t3_pri_con_04 + b2*t3_pri_con_05 + b3*t3_pri_con_06
t3_pri_con_f2 =~ 1*t3_pri_con_07 + c2*t3_pri_con_08 + c3*t3_pri_con_09

# error covariances
t3_pri_con_04 ~~ t2_pri_con_04 + t1_pri_con_04
t3_pri_con_05 ~~ t2_pri_con_05 + t1_pri_con_05
t3_pri_con_06 ~~ t2_pri_con_06 + t1_pri_con_06
t3_pri_con_07 ~~ t2_pri_con_07 + t1_pri_con_07
t3_pri_con_08 ~~ t2_pri_con_08 + t1_pri_con_08
t3_pri_con_09 ~~ t2_pri_con_09 + t1_pri_con_09
t2_pri_con_04 ~~ t1_pri_con_04
t2_pri_con_05 ~~ t1_pri_con_05 
t2_pri_con_06 ~~ t1_pri_con_06
t2_pri_con_07 ~~ t1_pri_con_07
t2_pri_con_08 ~~ t1_pri_con_08
t2_pri_con_09 ~~ t1_pri_con_09

# factor covariances
t1_pri_con_f ~~ t2_pri_con_f + t3_pri_con_f
t2_pri_con_f ~~ t3_pri_con_f
'
no <- no + 1
assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
```

### Reliability

```{r}
reliabilityL2(get(paste("fit", name, no, sep = "_")), paste("t1", name, "f", sep = "_"))
reliabilityL2(get(paste("fit", name, no, sep = "_")), paste("t2", name, "f", sep = "_"))
reliabilityL2(get(paste("fit", name, no, sep = "_")), paste("t3", name, "f", sep = "_"))
```

### Longitudinal Invariance

```{r}
(anova(get(paste("fit", name, no - 1, sep = "_")), get(paste("fit", name, no, sep = "_"))))
```

## Attitude Toward Online Sharing of Personal Information
### EFA

```{r}
no <- 0
name <- "inf_sha_att"
d_tmp <- select(d_wide, contains(paste0("t1_", name)), -contains("_m"))
model <- fa.parallel(d_tmp, fa = "fa", fm = "ml")
factan <- fa(d_tmp, fm = "ml", nfactors = model$nfact, rotate = "promax")
print(factan, sort = TRUE, cut = .3)
```

### CFA
#### First-Order Model Unconstrained

```{r}
model <- '
# create factors
t1_pri_con_f =~ 1*t1_pri_con_01 + t1_pri_con_02 + t1_pri_con_03 + t1_pri_con_04 + t1_pri_con_05 + t1_pri_con_06 + t1_pri_con_07 + t1_pri_con_08 + t1_pri_con_09
t2_pri_con_f =~ 1*t2_pri_con_01 + t2_pri_con_02 + t2_pri_con_03 + t2_pri_con_04 + t2_pri_con_05 + t2_pri_con_06 + t2_pri_con_07 + t2_pri_con_08 + t2_pri_con_09
t3_pri_con_f =~ 1*t3_pri_con_01 + t3_pri_con_02 + t3_pri_con_03 + t3_pri_con_04 + t3_pri_con_05 + t3_pri_con_06 + t3_pri_con_07 + t3_pri_con_08 + t3_pri_con_09

# error covariances
t3_pri_con_01 ~~ t2_pri_con_01 + t1_pri_con_01
t3_pri_con_02 ~~ t2_pri_con_02 + t1_pri_con_02
t3_pri_con_03 ~~ t2_pri_con_03 + t1_pri_con_03
t3_pri_con_04 ~~ t2_pri_con_04 + t1_pri_con_04
t3_pri_con_05 ~~ t2_pri_con_05 + t1_pri_con_05
t3_pri_con_06 ~~ t2_pri_con_06 + t1_pri_con_06
t3_pri_con_07 ~~ t2_pri_con_07 + t1_pri_con_07
t3_pri_con_08 ~~ t2_pri_con_08 + t1_pri_con_08
t3_pri_con_09 ~~ t2_pri_con_09 + t1_pri_con_09
t2_pri_con_01 ~~ t1_pri_con_01
t2_pri_con_02 ~~ t1_pri_con_02 
t2_pri_con_03 ~~ t1_pri_con_03
t2_pri_con_04 ~~ t1_pri_con_04
t2_pri_con_05 ~~ t1_pri_con_05 
t2_pri_con_06 ~~ t1_pri_con_06
t2_pri_con_07 ~~ t1_pri_con_07
t2_pri_con_08 ~~ t1_pri_con_08
t2_pri_con_09 ~~ t1_pri_con_09

# factor covariances
t1_pri_con_f ~~ t2_pri_con_f + t3_pri_con_f
t2_pri_con_f ~~ t3_pri_con_f
'
no <- no + 1
assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
```

#### First-Order Model Constrained

```{r}
model <- '
# create factors
t1_pri_con_f =~ 1*t1_pri_con_01 + a2*t1_pri_con_02 + a3*t1_pri_con_03 + a4*t1_pri_con_04 + a5*t1_pri_con_05 + a6*t1_pri_con_06 + a7*t1_pri_con_07 + a8*t1_pri_con_08 + a9*t1_pri_con_09
t2_pri_con_f =~ 1*t2_pri_con_01 + a2*t2_pri_con_02 + a3*t2_pri_con_03 + a4*t2_pri_con_04 + a5*t2_pri_con_05 + a6*t2_pri_con_06 + a7*t2_pri_con_07 + a8*t2_pri_con_08 + a9*t2_pri_con_09
t3_pri_con_f =~ 1*t3_pri_con_01 + a2*t3_pri_con_02 + a3*t3_pri_con_03 + a4*t3_pri_con_04 + a5*t3_pri_con_05 + a6*t3_pri_con_06 + a7*t3_pri_con_07 + a8*t3_pri_con_08 + a9*t3_pri_con_09

# error covariances
t3_pri_con_01 ~~ t2_pri_con_01 + t1_pri_con_01
t3_pri_con_02 ~~ t2_pri_con_02 + t1_pri_con_02
t3_pri_con_03 ~~ t2_pri_con_03 + t1_pri_con_03
t3_pri_con_04 ~~ t2_pri_con_04 + t1_pri_con_04
t3_pri_con_05 ~~ t2_pri_con_05 + t1_pri_con_05
t3_pri_con_06 ~~ t2_pri_con_06 + t1_pri_con_06
t3_pri_con_07 ~~ t2_pri_con_07 + t1_pri_con_07
t3_pri_con_08 ~~ t2_pri_con_08 + t1_pri_con_08
t3_pri_con_09 ~~ t2_pri_con_09 + t1_pri_con_09
t2_pri_con_01 ~~ t1_pri_con_01
t2_pri_con_02 ~~ t1_pri_con_02 
t2_pri_con_03 ~~ t1_pri_con_03
t2_pri_con_04 ~~ t1_pri_con_04
t2_pri_con_05 ~~ t1_pri_con_05 
t2_pri_con_06 ~~ t1_pri_con_06
t2_pri_con_07 ~~ t1_pri_con_07
t2_pri_con_08 ~~ t1_pri_con_08
t2_pri_con_09 ~~ t1_pri_con_09

# factor covariances
t1_pri_con_f ~~ t2_pri_con_f + t3_pri_con_f
t2_pri_con_f ~~ t3_pri_con_f
'
no <- no + 1
assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
```

#### Second-Order Model Unconstrained

We again run models in which we build sub-dimensions referring to the empirical EFA results and theoretical considerations. Resulting model fits the data better than unidimensional one.

```{r}
model <- '
# create factors
t1_inf_sha_att_f =~ 1*t1_inf_sha_att_f1 + t1_inf_sha_att_f2 + t1_inf_sha_att_f3 + t1_inf_sha_att_f4 + t1_inf_sha_att_f5
t2_inf_sha_att_f =~ 1*t2_inf_sha_att_f1 + t2_inf_sha_att_f2 + t2_inf_sha_att_f3 + t2_inf_sha_att_f4 + t2_inf_sha_att_f5
t3_inf_sha_att_f =~ 1*t3_inf_sha_att_f1 + t3_inf_sha_att_f2 + t3_inf_sha_att_f3 + t3_inf_sha_att_f4 + t3_inf_sha_att_f5
t1_inf_sha_att_f1 =~ 1*t1_inf_sha_att_01 + t1_inf_sha_att_02
t1_inf_sha_att_f2 =~ 1*t1_inf_sha_att_03 + t1_inf_sha_att_04
t1_inf_sha_att_f3 =~ 1*t1_inf_sha_att_05 + t1_inf_sha_att_06
t1_inf_sha_att_f4 =~ 1*t1_inf_sha_att_07 + t1_inf_sha_att_08
t1_inf_sha_att_f5 =~ 1*t1_inf_sha_att_10 + t1_inf_sha_att_11
t2_inf_sha_att_f1 =~ 1*t2_inf_sha_att_01 + t2_inf_sha_att_02
t2_inf_sha_att_f2 =~ 1*t2_inf_sha_att_03 + t2_inf_sha_att_04
t2_inf_sha_att_f3 =~ 1*t2_inf_sha_att_05 + t2_inf_sha_att_06
t2_inf_sha_att_f4 =~ 1*t2_inf_sha_att_07 + t2_inf_sha_att_08
t2_inf_sha_att_f5 =~ 1*t2_inf_sha_att_10 + t2_inf_sha_att_11
t3_inf_sha_att_f1 =~ 1*t3_inf_sha_att_01 + t3_inf_sha_att_02
t3_inf_sha_att_f2 =~ 1*t3_inf_sha_att_03 + t3_inf_sha_att_04
t3_inf_sha_att_f3 =~ 1*t3_inf_sha_att_05 + t3_inf_sha_att_06
t3_inf_sha_att_f4 =~ 1*t3_inf_sha_att_07 + t3_inf_sha_att_08
t3_inf_sha_att_f5 =~ 1*t3_inf_sha_att_10 + t3_inf_sha_att_11

# factor covariance
t1_inf_sha_att_f ~~ t2_inf_sha_att_f + t3_inf_sha_att_f
t2_inf_sha_att_f ~~ t3_inf_sha_att_f

# item error covariance
t1_inf_sha_att_01 ~~ t2_inf_sha_att_01 + t3_inf_sha_att_01
t2_inf_sha_att_01 ~~ t3_inf_sha_att_01
t1_inf_sha_att_02 ~~ t2_inf_sha_att_02 + t3_inf_sha_att_02
t2_inf_sha_att_02 ~~ t3_inf_sha_att_02
t1_inf_sha_att_03 ~~ t2_inf_sha_att_03 + t3_inf_sha_att_03
t2_inf_sha_att_03 ~~ t3_inf_sha_att_03
t1_inf_sha_att_04 ~~ t2_inf_sha_att_04 + t3_inf_sha_att_04
t2_inf_sha_att_04 ~~ t3_inf_sha_att_04
t1_inf_sha_att_05 ~~ t2_inf_sha_att_05 + t3_inf_sha_att_05
t2_inf_sha_att_05 ~~ t3_inf_sha_att_05
t1_inf_sha_att_06 ~~ t2_inf_sha_att_06 + t3_inf_sha_att_06
t2_inf_sha_att_06 ~~ t3_inf_sha_att_06
t1_inf_sha_att_07 ~~ t2_inf_sha_att_07 + t3_inf_sha_att_07
t2_inf_sha_att_07 ~~ t3_inf_sha_att_07
t1_inf_sha_att_08 ~~ t2_inf_sha_att_08 + t3_inf_sha_att_08
t2_inf_sha_att_08 ~~ t3_inf_sha_att_08
t1_inf_sha_att_10 ~~ t2_inf_sha_att_10 + t3_inf_sha_att_10
t2_inf_sha_att_10 ~~ t3_inf_sha_att_10
t1_inf_sha_att_11 ~~ t2_inf_sha_att_11 + t3_inf_sha_att_11
t2_inf_sha_att_11 ~~ t3_inf_sha_att_11
'
no <- no + 1
assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
```

#### Second-Order Model at All Waves Constrained

```{r}
model <- '
# create factors
t1_inf_sha_att_f =~ 1*t1_inf_sha_att_f1 + o2*t1_inf_sha_att_f2 + o3*t1_inf_sha_att_f3 + o4*t1_inf_sha_att_f4 + o5*t1_inf_sha_att_f5
t2_inf_sha_att_f =~ 1*t2_inf_sha_att_f1 + o2*t2_inf_sha_att_f2 + o3*t2_inf_sha_att_f3 + o4*t2_inf_sha_att_f4 + o5*t2_inf_sha_att_f5
t3_inf_sha_att_f =~ 1*t3_inf_sha_att_f1 + o2*t3_inf_sha_att_f2 + o3*t3_inf_sha_att_f3 + o4*t3_inf_sha_att_f4 + o5*t3_inf_sha_att_f5
t1_inf_sha_att_f1 =~ 1*t1_inf_sha_att_01 + j2*t1_inf_sha_att_02
t1_inf_sha_att_f2 =~ 1*t1_inf_sha_att_03 + k2*t1_inf_sha_att_04
t1_inf_sha_att_f3 =~ 1*t1_inf_sha_att_05 + l2*t1_inf_sha_att_06
t1_inf_sha_att_f4 =~ 1*t1_inf_sha_att_07 + m2*t1_inf_sha_att_08
t1_inf_sha_att_f5 =~ 1*t1_inf_sha_att_10 + n2*t1_inf_sha_att_11
t2_inf_sha_att_f1 =~ 1*t2_inf_sha_att_01 + j2*t2_inf_sha_att_02
t2_inf_sha_att_f2 =~ 1*t2_inf_sha_att_03 + k2*t2_inf_sha_att_04
t2_inf_sha_att_f3 =~ 1*t2_inf_sha_att_05 + l2*t2_inf_sha_att_06
t2_inf_sha_att_f4 =~ 1*t2_inf_sha_att_07 + m2*t2_inf_sha_att_08
t2_inf_sha_att_f5 =~ 1*t2_inf_sha_att_10 + n2*t2_inf_sha_att_11
t3_inf_sha_att_f1 =~ 1*t3_inf_sha_att_01 + j2*t3_inf_sha_att_02
t3_inf_sha_att_f2 =~ 1*t3_inf_sha_att_03 + k2*t3_inf_sha_att_04
t3_inf_sha_att_f3 =~ 1*t3_inf_sha_att_05 + l2*t3_inf_sha_att_06
t3_inf_sha_att_f4 =~ 1*t3_inf_sha_att_07 + m2*t3_inf_sha_att_08
t3_inf_sha_att_f5 =~ 1*t3_inf_sha_att_10 + n2*t3_inf_sha_att_11

# factor covariance
t1_inf_sha_att_f ~~ t2_inf_sha_att_f + t3_inf_sha_att_f
t2_inf_sha_att_f ~~ t3_inf_sha_att_f

# item error covariance
t1_inf_sha_att_01 ~~ t2_inf_sha_att_01 + t3_inf_sha_att_01
t2_inf_sha_att_01 ~~ t3_inf_sha_att_01
t1_inf_sha_att_02 ~~ t2_inf_sha_att_02 + t3_inf_sha_att_02
t2_inf_sha_att_02 ~~ t3_inf_sha_att_02
t1_inf_sha_att_03 ~~ t2_inf_sha_att_03 + t3_inf_sha_att_03
t2_inf_sha_att_03 ~~ t3_inf_sha_att_03
t1_inf_sha_att_04 ~~ t2_inf_sha_att_04 + t3_inf_sha_att_04
t2_inf_sha_att_04 ~~ t3_inf_sha_att_04
t1_inf_sha_att_05 ~~ t2_inf_sha_att_05 + t3_inf_sha_att_05
t2_inf_sha_att_05 ~~ t3_inf_sha_att_05
t1_inf_sha_att_06 ~~ t2_inf_sha_att_06 + t3_inf_sha_att_06
t2_inf_sha_att_06 ~~ t3_inf_sha_att_06
t1_inf_sha_att_07 ~~ t2_inf_sha_att_07 + t3_inf_sha_att_07
t2_inf_sha_att_07 ~~ t3_inf_sha_att_07
t1_inf_sha_att_08 ~~ t2_inf_sha_att_08 + t3_inf_sha_att_08
t2_inf_sha_att_08 ~~ t3_inf_sha_att_08
t1_inf_sha_att_10 ~~ t2_inf_sha_att_10 + t3_inf_sha_att_10
t2_inf_sha_att_10 ~~ t3_inf_sha_att_10
t1_inf_sha_att_11 ~~ t2_inf_sha_att_11 + t3_inf_sha_att_11
t2_inf_sha_att_11 ~~ t3_inf_sha_att_11
'
no <- no + 1
assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
```

### Reliability

```{r}
reliabilityL2(get(paste("fit", name, no, sep = "_")), paste("t1", name, "f", sep = "_"))
reliabilityL2(get(paste("fit", name, no, sep = "_")), paste("t2", name, "f", sep = "_"))
reliabilityL2(get(paste("fit", name, no, sep = "_")), paste("t3", name, "f", sep = "_"))
```

### Longitudinal Invariance

```{r}
(anova(get(paste("fit", name, no - 1, sep = "_")), get(paste("fit", name, no, sep = "_"))))
```

## Online Sharing of Personal Information
### EFA

```{r}
no <- 0
name <- "inf_sha_beh"
d_tmp <- select(d_wide, contains(paste0("t1_", name)), -contains("_m"))
model <- fa.parallel(d_tmp, fa = "fa", fm = "ml")
factan <- fa(d_tmp, fm = "ml", nfactors = model$nfact, rotate = "promax")
print(factan, sort = TRUE, cut = .3)
```

### CFA
#### First-Order Model Unconstrained

First-order model shows poor fit. Needs to be adapted (see second order model).

```{r}
model <- '
# create factors
t1_inf_sha_beh_f =~ 1*t1_inf_sha_beh_01 + t1_inf_sha_beh_02 + t1_inf_sha_beh_03 + t1_inf_sha_beh_04 + t1_inf_sha_beh_05 + t1_inf_sha_beh_06 + t1_inf_sha_beh_07 + t1_inf_sha_beh_08 + t1_inf_sha_beh_09 + t1_inf_sha_beh_10 + t1_inf_sha_beh_11
t2_inf_sha_beh_f =~ 1*t2_inf_sha_beh_01 + t2_inf_sha_beh_02 + t2_inf_sha_beh_03 + t2_inf_sha_beh_04 + t2_inf_sha_beh_05 + t2_inf_sha_beh_06 + t2_inf_sha_beh_07 + t2_inf_sha_beh_08 + t2_inf_sha_beh_09 + t2_inf_sha_beh_10 + t2_inf_sha_beh_11
t3_inf_sha_beh_f =~ 1*t3_inf_sha_beh_01 + t3_inf_sha_beh_02 + t3_inf_sha_beh_03 + t3_inf_sha_beh_04 + t3_inf_sha_beh_05 + t3_inf_sha_beh_06 + t3_inf_sha_beh_07 + t3_inf_sha_beh_08 + t3_inf_sha_beh_09 + t3_inf_sha_beh_10 + t3_inf_sha_beh_11

# factor covariance
t1_inf_sha_beh_f ~~ t2_inf_sha_beh_f + t3_inf_sha_beh_f
t2_inf_sha_beh_f ~~ t3_inf_sha_beh_f

# item error covariance
t1_inf_sha_beh_01 ~~ t2_inf_sha_beh_01 + t3_inf_sha_beh_01
t2_inf_sha_beh_01 ~~ t3_inf_sha_beh_01
t1_inf_sha_beh_02 ~~ t2_inf_sha_beh_02 + t3_inf_sha_beh_02
t2_inf_sha_beh_02 ~~ t3_inf_sha_beh_02
t1_inf_sha_beh_03 ~~ t2_inf_sha_beh_03 + t3_inf_sha_beh_03
t2_inf_sha_beh_03 ~~ t3_inf_sha_beh_03
t1_inf_sha_beh_04 ~~ t2_inf_sha_beh_04 + t3_inf_sha_beh_04
t2_inf_sha_beh_04 ~~ t3_inf_sha_beh_04
t1_inf_sha_beh_05 ~~ t2_inf_sha_beh_05 + t3_inf_sha_beh_05
t2_inf_sha_beh_05 ~~ t3_inf_sha_beh_05
t1_inf_sha_beh_06 ~~ t2_inf_sha_beh_06 + t3_inf_sha_beh_06
t2_inf_sha_beh_06 ~~ t3_inf_sha_beh_06
t1_inf_sha_beh_07 ~~ t2_inf_sha_beh_07 + t3_inf_sha_beh_07
t2_inf_sha_beh_07 ~~ t3_inf_sha_beh_07
t1_inf_sha_beh_08 ~~ t2_inf_sha_beh_08 + t3_inf_sha_beh_08
t2_inf_sha_beh_08 ~~ t3_inf_sha_beh_08
t1_inf_sha_beh_09 ~~ t2_inf_sha_beh_09 + t3_inf_sha_beh_09
t2_inf_sha_beh_09 ~~ t3_inf_sha_beh_09
t1_inf_sha_beh_10 ~~ t2_inf_sha_beh_10 + t3_inf_sha_beh_10
t2_inf_sha_beh_10 ~~ t3_inf_sha_beh_10
t1_inf_sha_beh_11 ~~ t2_inf_sha_beh_11 + t3_inf_sha_beh_11
t2_inf_sha_beh_11 ~~ t3_inf_sha_beh_11
'
no <- no + 1
assign(paste("fit", name, no, sep = "_"), cfa(model, d_wide, missing = "ML"))
summary(get(paste("fit", name, no, sep = "_")), standardized = TRUE, fit.measures = TRUE)
```

#### First-Order Model Constrained

>>>>

---
title: "List of Items"
output: 
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
---

@@
